---
title: "Female Incarceration Report"
author: "Kayla Tounalom"
date: "2/19/2022"
output: html_document
---
```{r setup, include=FALSE, warning = FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r,  include=FALSE, warning = FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
source("../source/analysis.R")
library(tidyverse)
library(dplyr)
library(maps)
```

In this report, I am analyzing incarceration data. The data I am analyzing is the comparison between black and white females incarceration population numbers. The reason I am specifically comparing the incarceration of females and not just the general population is there is a trend in data that showcases that there is an increase in incarceration throughout the U.S. it is important to look at incarceration data about females because there are implications that the outside world may or may not think of such as abuse, inadequate health checks (especially reproductive health), disruption in family relations and much more relating to female incarceration. With there being more females incarcerated over time it's important to bring awareness of issues or negatives that affect females who are incarcerated specifically. Now lets dive deeper into my report.


For my summary statistics, I calculated to find and compare the trend in data between black females and white females population who are incarcerated. For the whole data set, there is a total of `r format(obs_incarceration)` total rows and `r format(num_features_incarceration)` total columns. The incarceration data set ranges from **1970 to 2018**, however, the black female and white female incarcerated population data set ranges from **1970 to 2010**. Based on what I learned from the data set I decided to use the year **2000** and see how many black females were incarcerated compared to white females. What I saw was that there was a total of `r format(black_female_2000)`  incarcerated black females compared to white incarcerated females which were `r format(white_female_2000)`. The difference between black and white females incarcerated is 603.  This isn't a substantial difference however it is still important to look at. Another comparison I wanted to look at was the black female incarcerated population in the year **1970** compared to **2000**, what I saw was there was a total of `r format(black_female_1970)` black females incarcerated. This makes sense because collecting data in **1970** may not be accurate. To learn more about the data set I wanted to find out which state had the most female incarcerated population and the state was `r format(state_female_incarceration)` This does not surprise me because the population of New York is higher compared to other U.S. states. The last comparison I wanted to see was which state has the highest black female incarcerated population and I saw that `r format(highest_percent_femaleB)` while the state with the highest white female incarcerated population was `r format(highest_percent_femaleW)`.



### Chart 1: White Female Incarceration trend over time (1970-2010)
```{r  echo=FALSE, warning = FALSE,  message=FALSE}
ggplotly(chart_1)
```

In this chart, I am comparing the variables of white female incarceration over time from the span of **1970-to 2010.** As you can see from this chart there is an increase in incarceration rates. The chart shows that the number of white incarcerated females is over **40,000** in **2010.** 


### Chart 2: Black Female Incarceration trend over time. (1970-2010)
```{r  echo=FALSE, warning = FALSE,  message=FALSE}
ggplotly(chart_2)
```

In this chart, I decided to compare black females incarcerated over the span of **1970-2010** As you can see from this chart there is an upward trend of data throughout the years. Showcasing subtle dips but overall the population of black females incarcerated increases. The chart shows that the number of black incarcerated females is at a peak in **2010** however this dips. I believe there may be an inconsistency in the black female incarceration population. This could be because of several factors such as new laws and reforms and the policing system targeting certain populations of people such as black females. 

### Map: Black Female Incarceration in New York State
```{r echo=FALSE, warning = FALSE,  message=FALSE}
ggplotly(incarceration_map)
```
For this map, I decided to compare black female incarceration in New York State compared to other states because New York state has the most incarceration rates from this data set and for female incarceration. Based off the map, the highest incarceration number for Black Females is located in New York City as you can see. New York City is filled in with the color **red** indicating that it has the highest black female incarceration in the whole state. I suggest if you would like to look closer into New York City to zoom in, New York City is located at the bottom of the state.
