---
title: "Female Incarceration Report"
author: "Kayla Tounalom"
date: "2/19/2022"
output: html_document
---
```{r setup, include=FALSE, warning = FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r,  include=FALSE, warning = FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
source("../source/analysis.R")
library(tidyverse)
library(dplyr)
library(maps)
```

In this report, I am analyzing incarceration data. The data I am analyzing is the comparison between black and white females incarceration population numbers. The reason I am specifically comparing the incarceration of females and not just the general population is there is a trend in data that showcases that there is an increase in incarceration throughout the U.S. it is important to look at incarceration data about females because there are implications that the outside world may or may not think of such as abuse, inadequate health checks (especially reproductive health), disruption in family relations and much more relating to female incarceration. With there being more females incarcerated over time it's important to bring awareness of issues or negatives that affect females specifically.


For my summary statistics, I calculated to find and compare the trend in data between black females and white females population who are incarcerated. For the whole data set, there is a total of `r format(obs_incarceration)`total rows and **121** total columns. The incarceration data set ranges from **1970 to 2018**, however, the black female and white female incarcerated population data set ranges from **1970 to 2010**. Based on what I learned from the data set I decided to use the year **2000** and see how many black females were incarcerated compared to white females. What  I saw was that there was a total of **17,407** incarcerated black females compared to white females which were **18,010**. The difference between black and white females incarcerated is **603**.  This isn't a substantial difference however it is still important to look at. Another comparison I wanted to look at was the black female incarcerated population in the year **1970** compared to **2000**, what I saw was there was a total of **87** black females incarcerated. This makes sense because collecting data in **1970** may not be accurate. To learn more about the data set I wanted to find out which state had the most female incarcerated population and the state was **New York.** This does not surprise me because the population of New York is higher compared to other states. 



### Chart 1: White Female Incarceration trend over time (1970-2010)
```{r  echo=FALSE, warning = FALSE,  message=FALSE}
ggplotly(chart_1)
```

In this chart, I am comparing the variables of white female incarceration over time from the span of **1970-to 2010.** As you can see from this chart there is also an increase. The chart shows that the number of white incarcerated females is over **40,000** in **2010.** 


### Chart 2: Black Female Incarceration trend over time. (1970-2010)
```{r  echo=FALSE, warning = FALSE,  message=FALSE}
ggplotly(chart_2)
```

In this chart, I decided to compare black females incarcerated over the span of **1970-2010** As you can see from this chart there is an upward trend of data throughout the years. Showcasing subtle dips but overall the population of black females incarcerated increases. The chart shows that the number of black incarcerated females is at a peak in **2010** however this dips. I believe there may be an inconsistency in the black female incarceration population. This could be because of several factors such as new laws and reforms and the policing system targeting certain populations of people such as black females. 

### Map
```{r echo=FALSE, warning = FALSE,  message=FALSE}
ggplotly(incarceration_map)
```
